---
title: "myFirstRMarkdown"
author: "Ruizhou Peng"
date: "`r Sys.Date()`"
output: html_document
---

## 4. R Markdown

Firstly we create a data frame named animal_df

```{r}
animal <- c('snake', 'ostrich', 'cat', 'spider') 
nums_leg <- c(0, 2, 4, 8)

animal_df <- data.frame(animal, nums_leg)
```

then we print it

```{r}
print(animal_df)
```

see what will happen

## 5. Matrix operations

use seq() to generate vector

```{r}
x_vect <- seq(12, 2, -2)

```

convert vector into a matrix

```{r}
X <- matrix(x_vect, 2, 3)
```

create 2\*2matrix Y from 1-4

```{r}
Y <- matrix(seq(1,4,1), 2, 2)
```

create 2\*2matrix Z from 4-10

```{r}
Z <- matrix(seq(4,10,2), 2, 2) 
```

use t() to create transpos matrix of Y and Z

```{r}
YT <- t(Y)
ZT <- t(Z)
```

try matrix sums

```{r}
sum1 <- Y+Z
sum2 <- Z+Y
```

matrix multiplication: use %\*% not \*

```{r}
mul1 <- Y%*%Z
mul2 <- Z%*%Y
#mul3 <- Y*X
```

```{r}
res <- Y %*% X
```

matrix element-wise multiplication

```{r}
res2 <- Y*Z
res3 <- Z*Y
```

matrix inverse: use solve()

```{r}
Y_1 <- solve(Y)
check <- Y_1 %*% Y
Y_1X <- Y_1 %*% X
```

try Y^-1^ \* X without computing Y^-1^

```{r}
Y_1X_2 <- solve(Y, X)
```

### 6. R function

```{r}
myFirstRFunc <- function(n){
  "
  argument: n ---> number
  function: output the sum of those numbers strictly below n which are divisible by either 2 or 7 or both
  "
  
  sum <- 0
  iter <- 2
  while(iter<n){
    if(iter %% 7 == 0){
      iter <- iter+2
      next
    }

    sum <- sum + iter
    print(iter)
    iter <- iter + 2
    
  }
  iter <- 7
  while(iter < n){
    sum <- sum + iter
    print(iter)
    iter <- iter + 7

  }
  
  return(sum)
}

print(myFirstRFunc(15))
```

### 7. wave plot

```{r}
# define a vector x
x <- seq(0, 20, 0.01)

# define a vector y which equals sin(x)
y <- sin(x)

# create a data frame sin_df
sin_df <- data.frame(x = x,sinx = y)

# inspect first few rows
head(sin_df, 5)

# plot sin_df
plot(x, y, main = "sin(x)")
```

### 8. mathematical formula

$$ \sin(x)=\sum_{n=1}^{\infty}(-1)^{n+1}\cdot \frac{x^{2n-1}}{(2n-1)!} \approx x-\frac{x^3}{3!}+\frac{x^5}{5!}-\frac{x^7}{7!}\ldots.$$

$$
A=\left[\begin{matrix} a_{11} & a_{12}\\ a_{21} & a_{22} \end{matrix}\right]
$$
